Global code motion of congruent instructions

### 2017-04-18 paper.tex
fix

The compile time metrics of \GCM{} are listed in
Table~\ref{tab:code-motion-metric}. The table lists the number of scalars,
loads, stores and calls hoisted as well as removed. For each category, the
number of instructions removed is greater or equal to the number of instructions
hoisted because each hoisting is performed only when at least one identical
computation is found. Loads are hoisted the most followed by scalars, stores and
calls in decreasing order.  This was the common trend in all our
experiments. One reason why loads are hoisted the most is the early execution of
this pass (before mem2reg) in the \LLVM{} pass pipeline. Passes like mem2reg,
instcombine might actually remove those loads so this order may change should
this pass be scheduled later. The number of instructions sunk is very less
because \LLVM{} has a code sinking pass inside SimplifyCFG which runs before the
\GCM{} and sinks some instructions. Another reason is that instructions for which
dependencies are not directly available in the successor
(Section~\ref{subsec:legality-sink}) is not sunk for now. Sinking those
instructions would require a look ahead on the sinkability of the
dependencies. We plan to implement this in near future.

>>>>

The compile time metrics of \GCM{} are listed in
Table~\ref{tab:code-motion-metric}. The table lists the number of scalars,
loads, stores and calls hoisted as well as removed. For each category, the
number of instructions removed is greater or equal to the number of instructions
hoisted because each hoisting is performed only when at least one identical
computation is found. Loads are hoisted the most followed by scalars, stores and
calls in decreasing order.  This was the common trend in all our
experiments. One reason why loads are hoisted the most is the early execution of
this pass (before mem2reg) in the \LLVM{} pass pipeline. Passes like mem2reg and
instcombine might actually remove those loads and the number of hoisted loads may change should
the \GCM{} pass be scheduled later. The number of instructions sunk is very less
because \LLVM{} has a code sinking and hoisting transform inside SimplifyCFG pass which runs before
\GCM{} and sinks and hoists some instructions with some rather severe limitations. Another reason is that instructions for which
dependencies are not directly available in the successor
(Section~\ref{subsec:legality-sink}) is not sunk for now. Sinking those
instructions would require a look ahead on the sinkability of the
dependencies. We plan to implement this in near future.
